\Large {\bf rt1d: Documentation}

### 2012-06-06 doc/manual/rt1d_manual.tex
Trying to get finite-c working again...runs, needs more testing.  Other random cleanup too.
Working on finite c solver - error found in treatment of first cell.
Time-dependent SED stuff should now be handled via object age, instead of BH mass or whathaveyou.

\begin{verbatim}
import rt1d
import numpy as np
pf = rt1d.SetDefaultParameterValues()
r = np.linspace(3e19, 3e21, 100) # 100 grid cells between 0.01-1kpc. (optional)
data = rt1d.Shine(pf, r)    
\end{verbatim}

This would make it easy to:
\begin{itemize}
    \item Allow users to write their own rt1d `scripts.'
    \item Change source properties manually with time.
    \item Making arbitrarily structured grids.
    \item Very specific initial conditions.
\end{itemize}

@@

>>>>

\begin{verbatim}
import rt1d

pf = rt1d.SetDefaultParameterValues()
prob = rt1d.ProblemTypes.ProblemType(1)

for key in pf.keys():
    if key in prob.keys():
        pf[key] = prob[key]

pf["StopTime"] = 10

data, dt = rt1d.Shine(pf)   
\end{verbatim}

This would make it easy to:
\begin{itemize}
    \item Allow users to write their own rt1d `scripts.'
    \item Change source properties manually with time.
    \item Making arbitrarily structured grids.
    \item Very specific initial conditions.
    \item Run rad-hydro with \texttt{proteus}.
\end{itemize}

@@

%%%
%% Diffuse Radiation
%%%
\section{Diffuse Radiation}
Let's figure out where the on-the-spot approximation is pretty good.  This will depend on photon frequency, gas neutral fraction (of hydrogen and helium), and our grid resolution.

The optical depth along a ray is
\begin{align}
    \tau_{i,\nu} & = N_{i,\nu} \sigma_{i,\nu} \nonumber \\
    & = n_i dx \sigma_{i,\nu}
\end{align}    
where $n_i$ is the number density of absorbing species $i$, $\sigma_{i, \nu}$ is the bound-free absorption cross section for species $i$, and $dx$ is the length of the ray segment (i.e. our grid resolution). So, the total optical depth along this ray segment is
\begin{equation}
    \tau_{\nu} = \sum_i \tau_{i, \nu} .
\end{equation}    
If we assume that $\xHII = \xHeII$ and $\xHeIII = 0$, we can plot the ionized fraction vs. $\tau_{\nu}$ to get a handle on how good the OTSA is as a function of grid resolution and frequency.
